---
title: "Simple Linear Regression"
author: "Sakina Zaveri"
date: "24/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### **Calorie Cosumed data**

```{r echo=TRUE}

cal_data <- read.csv("D:\\DataScience\\simple_linear_regression\\calories_consumed.csv")

attach(cal_data)
View(cal_data)
summary(cal_data)

reg_cal <- lm(Weight.gained..grams. ~ Calories.Consumed)
plot(reg_cal)

summary(reg_cal)
```

### *Conclusion*

##### All the plots above shows the strong linearity between the two variables.
#### here the R^2 value of calorie_consumed data is greater than 0.85 which means that there is very strong correlation present between the variables / values.
##### R^2-value = 0.8968 > 0.85
##### correlation between the two variable shows that there is a strong relationship between the two variables and they are linear in the upward or in the positive direction.

### **Delivery Time**

```{r echo=TRUE}


delv_data <- read.csv("D:\\DataScience\\simple_linear_regression\\delivery_time.csv")

attach(delv_data)

plot(Sorting.Time,Delivery.Time)

head(delv_data)
View(delv_data)
summary(delv_data)

plot(Delivery.Time,Sorting.Time)
cor(Delivery.Time,Sorting.Time)
reg_delv <- lm(Delivery.Time ~ Sorting.Time)
summary(reg_delv)
confint(reg_delv,level = 0.95)
predict(reg_delv,interval = "predict")
# because our R^2 value is 0.6823 < 0.85 which means that there is a moderate correlation between the two variables.So we will transform our data to get the R^2 values near about 0.85 or >0.85.

#transforming the data we get.

reg_delv <- lm(Delivery.Time ~ log(Sorting.Time))
summary(reg_delv)

confint(reg_delv,level = 0.95)
predict(reg_delv,interval = "predict")
# we did'nt see much difference in the R^2 value which is 0.6954 still not strong relationship does it shows.

reg_delv <- lm(log(Delivery.Time) ~ Sorting.Time)
summary(reg_delv)
confint(reg_delv,level = 0.95)
predict(reg_delv,interval = "predict")

# we see much difference compared to orginal and the 1st transform we did in the R^2 value which is 0.7155 but still not strong relationship does it shows.here we can see that the error is much more than the two transformation we did.
```

### *Conclusion*

#### we can conclude that the sorting time is not acceptable we need to use other variable to get the best prediction model.

##**Emp data**

```{r echo=TRUE}

emp_data <- read.csv("D:\\DataScience\\simple_linear_regression\\emp_data.csv")
attach(emp_data)
View(emp_data)
head(emp_data)

plot(Salary_hike , Churn_out_rate )

emp_reg <- lm(Churn_out_rate ~ Salary_hike)
summary(emp_reg)
confint(emp_reg,level = 0.95)
predict(emp_reg,interval = "predict")
## here we see that the R^2 value is near to 0.85 but still < 0.85 so we will tranform our data to get the best R^2 value.

reg <- lm(Churn_out_rate ~ log(Salary_hike))
summary(reg)
confint(emp_reg,level = 0.95)
predict(emp_reg,interval = "predict")
## still the same as above. 

reg <- lm(log(Churn_out_rate) ~ Salary_hike)
summary(reg)
confint(emp_reg,level = 0.95)
predict(emp_reg,interval = "predict")

plot(reg)
## now the R^2 value is >0.85 which means that now are two variables have the strong relationship between than and shows the linearity 

```

#*Conclusion*
#### here we see that as there is a salary hike there will be decreased in churn out rate.
 
## **Salary Data**

```{r}
sal_data <- read.csv("D:\\DataScience\\simple_linear_regression\\Salary_Data.csv")
attach(sal_data)
head(sal_data)
plot(YearsExperience,Salary)
cor(YearsExperience , Salary)

reg_sal <- lm(Salary ~ YearsExperience)
summary(reg_sal)
plot(reg_sal)
## here we dont need to transform any data as its R^2 value is > 0.85 and shows a strong linearity realtionship 

```


#*Conclusion*
#### here we see that as there is a increase in experience there is increase in salary.
 