---
title: "Clustering Analysis"
author: "Sakina Zaveri"
date: "03/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Crime Data**

```{r echo=TRUE , fig.keep='all'}
crime_data <- read.csv("D:/DataScience/clustering/crime_data.csv",header = TRUE)

View(crime_data)

summary(crime_data)

## normalize the data
nor_data <- scale(crime_data[,2:5])

## distance matrix
d <- dist(nor_data , method = "euclidean")

## performing heirarichal clustering

fit <- hclust(d,method = "complete")

## creating dendrogram
plot(fit)
plot(fit , hang = -1)
rect.hclust(fit , k=6 , border = "red")

groups <- cutree(fit , k=6)
membership <- as.matrix(groups)

final <- data.frame(crime_data , membership)
View(final)
aggregate(crime_data[,2:5] , by = list(final$membership), FUN = mean )

## performing k-means clustering

## elbow curve to decide the k-value
wss = (nrow(nor_data)-1)*sum(apply(nor_data, 2,var))
for (i in 2:5) wss[i] = sum(kmeans(nor_data,centers = i)$withinss)
plot(1:5 ,wss, type = "b",xlab = "no. of clusters",ylab = "within group sums of squares",
     main = "k-means clustering scree plot")

## k value = 4 by seeing the scree plot
fit1 <- kmeans(nor_data,4)
str(fit1)

fit1$centers

##install.packages("animation")
library(animation)

km <- kmeans.ani(nor_data,4)


final1 <- data.frame(crime_data,fit1$cluster)
final1

View(final1)
aggregate(crime_data[,2:5] , by = list(fit1$cluster), FUN = mean )


```
### *Conclusion*

. while performing heirarichal clustering we found that that the crime rate is arranged from    maximum to minimum
. cluster formed in this data set are 4.


## **East West Airlines**
```{r echo=TRUE , fig.keep='all'}
library(xlsx)
air_data <- read.xlsx("D:/DataScience/clustering/EastWestAirlines.xlsx",sheetIndex = 2
                      ,header = TRUE)

View(air_data)

## structure of data
str(air_data)
summary(air_data)

## normalizing the data
data <- scale(air_data[,2:11])

## distance matrix
dis <- dist(data , method = "euclidean")

## performing heirarichal clustering

fit <- hclust(dis,method = "complete")
plot(fit)
plot(fit , hang=-1)

rect.hclust(fit , k=15 , border = "red")
rect.hclust(fit , k=25 , border = "red")

groups <- cutree(fit , k=15)
membership <- as.matrix(groups)

final <- data.frame(data , membership)
View(final)
aggregate(data , by = list(final$membership), FUN = mean )


## data set is too large to determine so using heirarichal clustering is in significant.
## data is not intrepreted
## performing k-means clustering

## elbow curve to decide the k-value
wss = (nrow(data)-1)*sum(apply(data, 2,var))
for (i in 2:8) wss[i] = sum(kmeans(nor_data,centers = i)$withinss)
plot(1:8 ,wss, type = "b",xlab = "no. of clusters",ylab = "within group sums of squares",
     main = "k-means clustering scree plot")

## through scree plot the 2 clusters will be good choice
## k-value = 2
km <- kmeans(data , 2)
str(km)

library(animation)
km1 <- kmeans.ani(data , 2)

final <- data.frame(data,km$cluster)
View(final)

aggregate(air_data[,2:12] , by = list(km$cluster), FUN = mean )


```

### *Conclusion*

.from the cluster analysis the outcome of this data set is that it is arranged in increasing  order the more the balance more the award you have .
.cluster formed in this dataset are 2.
